\begin{thebibliography}{9}

\bibitem{anwander07} Anwander, A., Tittgemeyer, M., von Cramon, D.Y., Friederici, A.D., Knösche, T.R., \emph{Connectivity-based parcellation of Broca's area.} \textit{Cereb Cortex} 17, 816-825. 2007. 

\bibitem{barch13} Barch, D. M., Burgess, G. C., Harms, M. P., Petersen, S. E., Schlaggar, B. L., Corbetta, M., et al. \emph{Function in the human connectome: Task-fMRI and individual differences in behavior.} \textit{Neuroimage} 80, 169–189. doi:10.1016/j.neuroimage.2013.05.033. 2013.

\bibitem{behrens03} Behrens, Johansen-Berg, Woolrich,  Smith, Wheeler-Kingshott, Barker, Sillery, Sheehan, Ciccarelli, Thompson, Brady, Matthews, \emph{No n-invasive mapping of connections between human thalamus and cortex using diffusion imaging}. \textit{Nat Neurosci} 6, 750-757. 2003.

\bibitem{brodman09} Brodmann,  K., \emph{Vergleichende  Lokalisationslehre  der  Großhirnrinde  in ihren Prinzipien dargestellt auf Grund des Zellaufbaues}. Barth, Leipzig. 1909. 

\bibitem{callaghan91} Callaghan P. T. , A. Coy, D. MacGowan, K. J. Packer, F. O. Zelaya. \emph{Diffraction-like effects in NMR diffusion studies of fluids in porous solids} \textit{Nature}; 351(6326):467-469. 1991.

\bibitem{descoteaux09} Descoteaux, M., Deriche, R., Knösche, T., \& Anwander, A. (2009). \emph{Deterministic and Probabilistic Tractography Based on Complex Fiber Orientation Distributions}. \textit{IEEE Transactions on Medical Imaging}, 28(2), 269–286.

\bibitem{greicius02} Michael D. Greicius, Ben Krasnow, Allan L. Reiss and Vinod Menon. \emph{Functional connectivity in the resting brain: A network analysis of the default mode hypothesis}. Washington University School of Medicine. 2002.

\bibitem{hartigan79} Hartigan, J. A.; Wong, M. A. \emph{Algorithm AS 136: A K-Means Clustering Algorithm}. \textit{Journal of the Royal Statistical Society, Series C} 28 (1): 100–108. JSTOR 2346830. 1979.

\bibitem{hastie09} Hastie, Trevor; Tibshirani, Robert; Friedman, Jerome. \emph{The Elements of Statistical Learning}. New York: Springer. pp. 236-243. ISBN 0-387-84857-6. 2009.

\bibitem{hastie09b} Hastie, Trevor; Tibshirani, Robert; Friedman, Jerome. \emph{The Elements of Statistical Learning}. New York: Springer. pp. 520–528. ISBN 0-387-84857-6. 2009.

\bibitem{jbabdi14} Jbabdi, S., Woolrich, M. W., Andersson, J. L. R., \& Behrens, T. E. J. (2007). \emph{A Bayesian framework for global tractography.}, \textit{NeuroImage}, 37(1), 116–129. doi:10.1016/j.neuroimage.2007.04.039.

\bibitem{moreno14} Moreno-Dominguez D., Anwander A, Knösche TR \emph{A hierarchical method for whole-brain connectivity-based parcellation.}, \textit{Hum Brain Mapp}, 35(10):5000-25. doi: 10.1002/hbm.22528. Epub 2014.

\bibitem{pohl07} Pohl KM1, Fisher J, Bouix S, Shenton M, McCarley RW, Grimson WE, Kikinis R, Wells WM. \emph{Using the logarithm of odds to define a vector space on probabilistic atlases}. \textit{Med Image Anal}. 11(5):465-77. 2007.

\bibitem{stejskal65} Stejskal, E. O.; Tanner, J. E. \emph{Spin Diffusion Measurements: Spin Echoes in the Presence of a Time-Dependent Field Gradient}. \textit{The Journal of Chemical Physics} 42 (1): 288. 1965

\bibitem{tournier04} Tournier, J.D., Calamante, F., Gadian, D.G., Connelly, A., \emph{Direct estimation of the fiber orientation density function from diffusion-weighted MRI data using spherical deconvolution.} \textit{Neuroimage} 23, 1176–1185. 2004.

\bibitem{tuch04} Tuch D. S., \emph{Q-ball  imaging} \textit{Magn. Reson. Med.} ;52;6, 1358–1372. 2004.

\bibitem{Lipton2014} Michael L. Lipton [Albert Einstein College of Medicine]. Introducing MRI [Video file]. Retrieved from https://www.youtube.com/watch?v=35gfOtjRcic. 2014. 




\end{thebibliography}


